---
title: "Epidemia simulation - Best case scenario (for finding an effect of EURO2020)"
author: "Johannes Enevoldsen"
date: "8/25/2021"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.path = "figures/")
options(mc.cores = parallel::detectCores())
```

```{r}
library(tidyverse)
library(epidemia)
library(lubridate)
```

The idea here is to create a very strict simulation of what data would look like if R(t) only varies with Delt% and on match days, and if every infected test positive withing ~2-10 days.

# Prepare data
First we get some data. 

```{r}
cases <- read_csv(here::here("input/analysis.csv")) %>%
    mutate(week = week(date),
           wday = factor(wday(date, label = TRUE, week_start = 1), ordered = FALSE),
           masks = factor(masks),
           gatherlim = factor(gatherlim),
           ntests_sqrt = sqrt(ntests),
           newcases = ifelse(date < (min(date) + 15), NA, newcases))

cases_dk <- filter(cases, country == "denmark",
                   date > dmy("01-06-2021") - 15,
                   date < dmy("25-07-2021"))

cases_dk$newcases[1:15] <- NA

# convenient layers for plotting
geom_match_line <- geom_vline(xintercept = cases_dk$date[cases_dk$match == 1])

# Remove the days used for seeding the model
scale_x_rm_seed <- scale_x_date(limits = c(min(cases_dk$date[!is.na(cases_dk$newcases)]),
                                         max(cases_dk$date[!is.na(cases_dk$newcases)])), 
                                date_minor_breaks = "1 day")

ggplot(cases_dk, aes(date, newcases)) +
    geom_line() +
    geom_match_line +
    scale_x_rm_seed 
```

# Setup simple epidemia model

```{r}
serial_interval <- EuropeCovid2$si
plot(serial_interval)
inf2test <- dlnorm(1:20, log(5), log(1.4))
inf2test_1 <- inf2test / (sum(inf2test)) # Make it sum to 1
plot(inf2test_1)

rt <- epirt(formula = R(country, date) ~ 1 + match +
                #masks + gatherlim + # restriction
                perc_sequences,
                #rw(prior_scale = 0.05)
            prior = normal(log(5), 0.1),
            prior_intercept = normal(log(2), 0.2), link = 'log')

obs <-  epiobs(formula = newcases ~ 1, #+ wday, #+ ntests_sqrt,# + offset(rep(1,93)),
               link = "identity",
               i2o = inf2test_1,
               #prior = normal(1.1, 0.2),
               prior = normal(5, 0.2), # we catch all cases
               ) # 75% of infected test positive

inf <- epiinf(gen = serial_interval,
              prior_seeds = normal(1000, 1500),
              seed_days = 15)

```


# Fit model

```{r, echo=FALSE, message = FALSE}
args <- list(rt = rt, obs = obs, inf = inf, data = cases_dk, iter = 1e3,
             seed = 12345)

fm_dk <- do.call(epim, args)

```

## Predicted positive test given the fitted model

```{r}
plot_obs(fm_dk, type = "newcases") + 
    geom_match_line +
    scale_x_rm_seed
```

## R(t) given the fitted model

```{r}
plot_rt(fm_dk) +
    scale_x_rm_seed
```

## Infections predicted by the model

```{r}
plot_infections(fm_dk) + 
    scale_x_rm_seed
```

The model assumes a huge effect from the matches.

# Simulate positive tests with the model

Now we look at how many positive tests we should expect each day with this very large number of infected on match days. We create just 6 simulations.

```{r}
sim_dk <- posterior_predict(fm_dk, draws = 6)

sim_dk_samp <- tibble(time = sim_dk$time, newcases = as.data.frame(aperm(sim_dk$draws, c(2,1)))) %>% 
    unpack(newcases, names_sep = "_") %>% 
    pivot_longer(starts_with("newcases"), values_to = "newcases", names_to = "sim")
ggplot(sim_dk_samp, aes(time, newcases, groups = sim)) +
    geom_line() +
    geom_match_line +
    scale_x_rm_seed + 
    facet_wrap(~sim, ncol = 2)  
```

We can also do 200...
```{r}
sim_dk <- posterior_predict(fm_dk, draws = 200)

sim_dk_samp <- tibble(time = sim_dk$time, newcases = as.data.frame(aperm(sim_dk$draws, c(2,1)))) %>% 
    unpack(newcases, names_sep = "_") %>% 
    pivot_longer(starts_with("newcases"), values_to = "newcases", names_to = "sim")
ggplot(sim_dk_samp, aes(time, newcases, color = sim)) +
    geom_line(alpha = 0.2, show.legend = FALSE) +
    geom_match_line +
    scale_x_rm_seed
```

Basically, the uncertainty in dispersion in time from infected to positive test washes out the very high infection rate at each match day.
